Prey skill shapes the acquisition of predator expertise in a virtual bi-trophic system

### 2025-05-26 manuscript/manuscript.Rmd
Windows --> figx now fig2
Windows --> correct fig2
load proper loo file

# Open the loo table
path <- file.path(here::here("outputs", "outputs_model-validation"))
loo_tab <- data.table(readRDS(file.path(path, "GAMM_loo-cv-table.rds")))

@@

knitr::include_graphics(
  here::here("outputs", "outputs_figures", "figurex.png")
)
```

@@

>>>>

# Open the loo table
path <- file.path(here::here("outputs", "outputs_model-validation"))
loo_tab <- data.table(readRDS(file.path(path, "loo-cv-table_GAMM.rds")))

@@

@@

knitr::include_graphics(
  here::here("outputs", "outputs_figures", "figure3.png")
)
```
